An Analysis on the Impact of Local Food Choices

### 2020-03-21 paper_pdf.Rmd

## Summary statistics of all the local stores/ food choices variables (on county level)
```{r, my-fig,out.width = '80%', fig.cap = "descriptive statistics", echo = FALSE}
knitr::include_graphics('/images/descriptive_food/descriptive.png')
```
As can be seen from the table, Convenience stores got very high values of availabilities per capita, while Supercenters & Club Stores, Specialized Food Stores and Farmers’ Markets got relatively low values.

@@

```{r, my-fig3,out.width = '90%',echo = FALSE,fig.cap = "convenience store trend"}
knitr::include_graphics('/images/tableau_food/1/Dashboard 2.png')
```

@@

```{r, my-fig4,out.width = '90%',echo = FALSE,fig.cap = "Obesity rate 2008 and 2013"}
knitr::include_graphics('/images/descriptive_food/obesity.png')
```

@@

# Appendix

>>>>

## Summary statistics of all the local stores/ food choices variables (on county level)
```{r, my-fig,out.width = '80%', fig.cap = "descriptive statistics", echo = FALSE}
knitr::include_graphics('images/descriptive_food/descriptive.png')
```
As can be seen from the table, Convenience stores got very high values of availabilities per capita, while Supercenters & Club Stores, Specialized Food Stores and Farmers’ Markets got relatively low values.

@@

```{r, my-fig3,out.width = '90%',echo = FALSE,fig.cap = "convenience store trend"}
knitr::include_graphics('images/tableau_food/1/Dashboard 2.png')
```

@@

```{r, my-fig4,out.width = '90%',echo = FALSE,fig.cap = "Obesity rate 2008 and 2013"}
knitr::include_graphics('images/descriptive_food/obesity.png')
```

@@

# Appendix
```{r, my-fig18,out.width = '90%',echo = FALSE,fig.cap = "convenience store map"}
knitr::include_graphics('images/tableau_food/2/Dashboard 1.png')
```

```{r, my-fig5,out.width = '90%',echo = FALSE,fig.cap = "Fast food trend"}
knitr::include_graphics('images/tableau_food/2/Dashboard 2.png')
```

```{r, my-fig6,out.width = '90%',echo = FALSE,fig.cap = "wic map"}
knitr::include_graphics('images/tableau_food/3/Dashboard 1.png')
```

```{r, my-fig7,out.width = '90%',echo = FALSE,fig.cap = "wic trend"}
knitr::include_graphics('images/tableau_food/3/Dashboard 2.png')
```

```{r, my-fig8,out.width = '90%',echo = FALSE,fig.cap = "super center map"}
knitr::include_graphics('images/tableau_food/4/Dashboard 1.png')
```

```{r, my-fig9,out.width = '90%',echo = FALSE,fig.cap = "super center trend"}
knitr::include_graphics('images/tableau_food/4/Dashboard 2.png')
```

```{r, my-fig10,out.width = '90%',echo = FALSE,fig.cap = "specialized food store map"}
knitr::include_graphics('images/tableau_food/5/Dashboard 1.png')
```

```{r, my-fig11,out.width = '90%',echo = FALSE,fig.cap = "specialized food store trend"}
knitr::include_graphics('images/tableau_food/5/Dashboard 2.png')
```

```{r, my-fig12,out.width = '90%',echo = FALSE,fig.cap = "Farmer's market map"}
knitr::include_graphics('images/tableau_food/6/Dashboard 1.png')
```

```{r, my-fig13,out.width = '90%',echo = FALSE,fig.cap = "Farmer's market trend"}
knitr::include_graphics('images/tableau_food/6/Dashboard 2.png')
```

```{r, my-fig14,out.width = '90%',echo = FALSE,fig.cap = "Grocery store map"}
knitr::include_graphics('images/tableau_food/7/Dashboard 1.png')
```

```{r, my-fig15,out.width = '90%',echo = FALSE,fig.cap = "Grocery store trend"}
knitr::include_graphics('images/tableau_food/7/Dashboard 2.png')
```

```{r, my-fig16,out.width = '90%',echo = FALSE,fig.cap = "Recreational facilities map"}
knitr::include_graphics('images/tableau_food/8/Dashboard 1.png')
```

```{r, my-fig17,out.width = '90%',echo = FALSE,fig.cap = "Recreational facilities trend"}
knitr::include_graphics('images/tableau_food/8/Dashboard 2.png')
```
